### 2010-10-30 doc/tech_doc/a-rex/arex_tech_doc.tex
New limit on total number of jobs implemented

{[}max\_running\_jobs {[}max\_jobs\_per\_dn]]]} -- specifies maximum number of
jobs being processed by the A-REX at different stages:\\

@@

processed is still \textit{max\_processed\_jobs}.

>>>>

{[}max\_running\_jobs {[}max\_jobs\_per\_dn {[}max\_jobs\_total]]]]} -- specifies 
maximum number of jobs being processed by the A-REX at different stages:\\

@@

processed is still \textit{max\_processed\_jobs}.\\
\textit{max\_jobs\_total} -- total maximum number of jobs associated with 
service. It is advised to use this limit only inexceptional case because
it also accounts for finished jobs.\\
